Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-03-23 supplement.tex
Update
Fill in supmat

\richel{Issue at \url{https://github.com/richelbilderbeek/pirouette_article/issues/75}}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/example_28/errors.png}
  \caption{Error distribution from a distribution of trees}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_20/example_20/errors.png}
  \caption{10 taxa}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_20/example_20/315/errors.png}
  \caption{20 taxa}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_20/example_20/316/errors.png}
  \caption{30 taxa}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_20/example_20/317/errors.png}
  \caption{40 taxa}
\end{figure}

@@

The main example uses a DNA alignment length of \richel{?} nucleotides.
One expects that the more nucleotides are present in the alignment,
the more information is available,
thus the better the inference will be, 
thus the lower the errors will be.
Here, we show the same results as the main example,
except for a varying DNA alignment sequence length.

>>>>

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_28/errors.png}
  \caption{Error distribution from a distribution of trees}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_20/errors_5.png}
  \caption{5 taxa}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_20/errors_10.png}
  \caption{10 taxa}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_20/errors_20.png}
  \caption{20 taxa}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_20/errors_30.png}
  \caption{30 taxa}
\end{figure}

@@

The main example uses a DNA alignment length of 1000 nucleotides.
One expects that the more nucleotides are present in the alignment,
the more information is available,
thus the better the inference will be, 
thus the lower the errors will be.
Here, we show the same results as the main example,
except for a varying DNA alignment sequence length.
